---
title: "Homework 1"
author: "GVPT 729A"
date: "9/14/2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


In this homework assignment you will compare estimates of a sample mean using MLE to Least Squares.  Below is a likeihood function for the OLS model with no covariates.  You can use this function calculate the MLE for the mean ($\mu$).

```{r}
my.ols <- function(mu, y) {-sum((y - mu)^2)}

ols.mle <- function(y) {
  est <- optim(par = 0, fn = my.ols, y = y,
               control = list(fnscale = -1),
               method = "Brent",  # for 1d problems
               lower = -100, upper = 100)
  res <- list(est = est$par)
  return(res)
}
```

You should write a Monte Carol simulation and compare your estimates of $\hat{\mu}$ and $sd(\hat{\mu})$ for the MLE and the Least Squares calculation (for the Least Squares calculation you can use lm(y~)). Produce two sets of simulations: the first set with two different sample sizes; the second set with two different number of replications. Your results will be sensitive to the sample size and number of replications you use in your Monte Carlo experiment. Please comment on this.

You can turn in the assignment via email or hard copy. Don't forget to include your code and results. 
